\chapter{The Scuba days}

Hey Dad,

It's been a few years since I got into the water, but a friend of mine recently told me he had never gone diving before.
Absurd, right?
I had to show him around, so I dusted off the old dry suits and jumped in...


Every time I go for a dive, I find something interesting.
When I was younger, I found all the animals...
But today, I found something I never thought I would see: a solar panel from a satellite -- almost completely in-tact!

They say that when people who grew up around the ocean 

I've been swimming again recently with Ryan.
I \textit{think} you two met a long time ago, but I doubt you would remember him.
He's changed a lot since we were kids.

Honestly, I took a break from the sea almost entirely while Leia was growing up.
I mean, there are jellyfish and sharks and octopi... Just any number of things that could kill me, and with Joanne out of the picture, I didn't feel comfortable swimming alone.

Still, some of my fondest memories were swimming with you when we I was younger.

You know the island a few kilometers from shore?
The one with the lighthouse and Johnny?
We used to swim there all the time.
Ryan and I decided to go there the other day and we were immediately kicked out because it was ``private property.''

I guess Johnny passed away without telling anyone and now the lighthouse has a full staff of people -- none of whom knew either of us.

There's a certain magic to swimming in an endless sea with a school of fish in your wake.

At the same time, I was terrified.
At that scale, the fish might as well have been locusts.

GPS lost
