\chapter{Scribblings}

\chapter{In the twilight hours}

To be honest, I have never written anything in my life.
Well, nothing worth noting anyway.
There was one time in high school where I wanted to be a poet and tried to write a poem a day, but my father beat that out of me real quick.

As such, I'm not exactly sure why I'm writing this or even who I am writing this for.
All I know is that my daughter is off to bigger and better things, and I'm an emotional wreck.
Writing helps alleviate the pain, if only slightly.

It also helps me...

I like to think of myself as a rational man.
The type of person who thinks through everything that he does and only acts after careful consideration, but to be honest, that sounds more like my father.
He didn't cry...


I cannot say I've lived a happy life.
It wasn't unhappy either.
It's just that no matter how hard I tried, I couldn't rock my own boat.


\section{My father}

In the eyes of a child, a stick can be a sword, gun, shield, or wand... Really anything you need to tell a compelling story.
At that age, imagination is limitless and the fewer limitations on your own creativity, the better.
I grew up no limitations.
In fact, in an era where technology creeped itself into every facet of existence, I found myself disconnected from reality.

We lived in a small, relatively poor town on an island quite far from the mainland, and as such everyone lived modestly.
On the days where I was not adventuring with my schoolmates or helping my father with his fishing ventures, I was probably in the library, reading whatever I could find.

Moreover, my father was always fascinated by somewhat ancient technology.
While every other fisherman happily used GPS, he was insistent on charting the stars.
He prided himself on how he had lived his entire life without a smart phone and refused to use any devices with touch screens out of pure spite.
He even refused to buy any sort of TV or computer for our house, saying that the library was all the entertainment I would ever need.



Throughout my years as a fisherman, I have developed a single, cardinal rule: don't drive in twilight.
Once the satellites are out, navigation is nearly impossible.

When I was younger, before the catastrophe...


\section{My wife}

The loss of my father lead to the loss of my wife.


\section{My daughter}

Have you ever boiled beans?
I think I can describe my daughter's entire personality in a single conversationwe had when she was 10:

``Why do beans float?''

``What?''

``Like when you boil them. Why do beans float for a bit and then sink back down?'' She paused before continuing, ``Like, to float, it needs to be less dense than water. The beans are more dense in cold water. Less dense in boiled water. Then more dense again after everything settles down.''


\section{My life}

I cannot say I've lived a happy life.
It wasn't unhappy either.
It's just that no matter how hard I tried, I couldn't rock my own boat.

But now there's hope.
Hope that one day, I'll be able to watch the stars and that one of them might even be my daughter
